\section{Exercise 8.7 Make amends}
\textbf{Problem:} Find an \textit{interesting applied problem}, model it as a pure- or mixed-\textit{integer} linear-optimization problem, and test your model with AMPL. Credit will be given for \textit{deft} modeling, \textit{sophisticated} use of AMPL, testing on meaningfully-\textit{large} instances, and \textit{insightful} analysis. Try to play with CPLEX \textit{integer} solver options (they can be set through AMPL) to get better behavior of the solver.

\textbf{Solution:} 

We construct the following problem as an example. Suppose Martin wants to make money and he decides to open several restaurants in the city he lives. There are 4 types of restaurants, 
\begin{itemize}
\item Japanese restaurant needs 20 employees each and has a profit of \$ 420.5 per day;
\item Chinese restaurant needs 17 employees each and has a profit of \$ 325.6 per day;
\item Italian restaurant needs 27 employees each and has a profit of \$ 507.2 per day;
\item French restaurant needs 30 employees each and has a profit of \$ 486.3 per day;
\end{itemize}

Martin would like to open at least 77 restaurants but he only has 813 people to serve in restaurants. For unemployed people, he needs to pay \$ 5.7 per person. The goal is to maximize the profit of all restaurants. 

This is an optimization problem and can be formalized as follows:
\begin{equation}
\label{eq: martin}
  \begin{array}{lrcll}
    \max
    & \multicolumn{4}{l}{420.5x_1+325.6x_2+507.2x_3+486.3x_4} \\
    \text{s.t.}
    & x_1+x_2+x_3+x_4\geq{}77; \\
    & 20x_1+17x_2+27x_3+30x_4\leq{}813; \\
    & x_1 \geq 0 \text{ and integer};\\
    & x_2 \geq 0 \text{ and integer};\\
    & x_3 \geq 0 \text{ and integer};\\
    & x_4 \geq 0 \text{ and integer}.\\
  \end{array}
\end{equation}

The AMPL file ex8\_7.mod is attached at follows,
\bigskip
\hrule 
\small
\verbatiminput{p7/ex8.7/ex8_7.mod}
\normalsize
\hrule
\bigskip

The AMPL file ex8\_7.dat is attached at follows,
\bigskip
\hrule 
\small
\verbatiminput{p7/ex8.7/ex8_7.dat}
\normalsize
\hrule
\bigskip

The AMPL file ex8\_7.run is attached at follows,
\bigskip
\hrule 
\small
\verbatiminput{p7/ex8.7/ex8_7.run}
\normalsize
\hrule
\bigskip
